WORCS: A Workflow for Open Reproducible Code in Science

### 2020-10-31 paper/Manuscript_DS.Rmd
R3 C2: Non-linear

We provide a conceptual outline of the WORCS procedure below, based on WORCS
Version 0.1.2. 
For users of the `worcs` `R` package, we highly recommend referring to
[the workflow vignette](https://cjvanlissa.github.io/worcs/articles/setup.html),
which is more detailed and updated with future developments.

>>>>

We provide a conceptual outline of the WORCS procedure below, based on WORCS
Version 0.1.5.
Note that, although the steps are numbered for reference purposes,
we acknowledge that the process of conducting research is not always linear.
For users of the `worcs` `R` package, we highly recommend referring to
[the workflow vignette](https://cjvanlissa.github.io/worcs/articles/setup.html),
which is more detailed and updated with future developments.

### 2020-10-31 paper/reviews_ds.Rmd
R3 C2: Non-linear

Response: Opinions? I don't think this is entirely true. Nothing prevents researchers from going back and changing stuff? Or are there specific bottlenecks?

>>>>

Response: We agree with the Reviewer that researchers often go back and forth in their work. We did not intend to convey the impression that the process of conducting research is assumed to be linear. Of course, since we are presenting a workflow - there are a number of steps involved, which we have placed in a sensible order. For example, Study Design must logically occur prior to Writing and Analysis, and Publication can only logically occur after Writing. We also wish to emphasize that the "tool" (we assume the Reviewer is referring to the `worcs` R-package) does not enforce any kind of linearity.

To address the Reviewer's comment, we have made two changes: First, we now explicitly state, in the paper and the Workflow vignette, that the steps are not necessarily linear. Second, while it was always possible to manually add a manuscript or preregistration at a later point in time after creating a new project in RStudio - we have now added functions to increase the non-linear flexibility of the `worcs` package: `add_manuscript()` and `add_preregistration()`.
